---
title: "Let's Play Monopoly!"
output: word_document
date: "2023-03-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## libraries
```{r, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyverse)
```


## Monopoly Movement Rules!
- Before starting the game, it is important to take note of the different types of "equipment" in Monopoly.

### Equipment
#### The Board
- The Board consists of...
  - 40 tiles, each of which have unique actions associated with them based on their type.
  - 16 "CHANCE CARDS"
  - 16 "COMMUNITY CHEST CARDS"
  - 2 six-sided dice

#### Types of Tiles
- "PROPERTY" Tiles
  - There are 8 different sets of properties
  - Each set of properties has...
      - its own color
      - 2 or 3 properties
  - These tiles can bought
  - Each of these tiles have a specialized cost/profit associated with them
  - **These tiles can generate a profit**
  
- "RAILROAD" Tiles
  - There are 4 different railroads evenly spaced across the Board
  - These tiles can be bought
  - Each of these tiles have a specialized cost/profit associated with them
  - **These tiles can generate a profit**
  
- "UTILITY" Tiles
  - There are two utility tiles
  - These tiles can be bought
  - Each of these tiles have a specialized cost/profit associated with them
  - **These tiles can generate a profit**
  
- "CHANCE" Tiles
  - There are 3 chance tiles
  - If one of these tiles is landed on, a "CHANCE CARD" is drawn
    - each of these cards has a specialized action associated with them
    
- "COMMUNITY CHEST" Tiles
  - There are 3 community chest tiles
  - If one of these tiles is landed on, a "COMMUNITY CHEST CHEST" is drawn
    - each of these cards has a specialized action associated with them
    
- "TAX" Tiles
  - There are 2 tax tiles
  - Each of these tiles has a cost associated with them
  
- "GO"
  - This is the first tile
  - Every time this tile is landed on or passed the player collects "$200"
  
- "IN JAIL"

- "GO TO JAIL"
  - When landed on, the player is moved to "IN JAIL"
  
- "FREE PARKING"

### Moving around the Board and Generating Profits

- The first step for beginning the game, even before getting to move the first game piece, is to determine which player will move first.
  - To do this, each player will roll both dice and find the sum of the rolls. The player with the largest sum will start the game. Then the following turn will be the next player.
    - i.e. if Player 2 starts, Player 3 will go next, then Player 4, then Player 4, then back to Player 2, and so on...
    
- All players will start on the "GO" tile.

- To determine how many spaces to move, on their turn each player will roll both dice and find the sum of the rolls. They will then move forward that number of tiles.
  - In the special case of rolling "doubles" (the roll of each die are equal),
      - the player will find the sum of rolls and move forward this number of tiles
      - then, the player will roll again and repeat the previous step.
        - If the player rolls "doubles" again, repeat the previous two steps.
        - If the player rolls "doubles" three times in a row, they immediately move to the "IN JAIL" tile.

- After moving to their next location, the player will have different actions to complete based on the tile type.

  - A player lands on a "PROPERTY" tile...
    - If the player is the first person to land on the "PROPERTY" tile they can buy the "PROPERTY"
    - Then, every time another player lands on this "PROPERTY", the player has to pay a fee and **the "PROPERTY" generates a profit**
        - This profit is based on the rent of the "PROPERTY"
    
  - A player lands on a "RAILROAD" tile...
    - If the player is the first person to land on the "RAILROAD" tile they can buy the "RAILROAD"
    - Then, every time another player lands on this "RAILROAD", the player has to pay a fee and **the "RAILROAD" generates a profit**
      - This profit is based on the number of "RAILROAD" tiles owned 
   
  - A player lands on a "UTILITY" tile...
      - If the player is the first person to land on the "UTILITY" tile they can buy the "UTILITY"
    - Then, every time another player lands on this "UTILITY", the player has to pay a fee and **the "UTILITY" generates a unique profit**
      - This profit is based on the sum of the dice rolled
      
  - A player lands on a "CHANCE" or "COMMUNITY CHEST" tile...
    - The player draws either a "CHANCE" or "COMMUNITY CHEST" card based on the type tile they landed on
      - Then, the player completes the action on the card
    - **These tiles cannot be bought and cannot generate a profit**
    
  - A player lands on a "TAX" tile...
    - The player must pay a fee unique to the tile
    - **These tiles cannot be bought and cannot generate a profit**

  - A player lands on or passes "GO"...
    - The player collects "$200"
    - **This tile cannot be bought and cannot generate a profit**
    
  - A player lands on "IN JAIL"...
    - There is no action to be completed
    - **This tile cannot be bought and cannot generate a profit**
    
  - A player lands on "GO TO JAIL"...
    - The player is immediately moved to "IN JAIL"
    - The player is unable to move forward for the next three rolls
    - **This tile cannot be bought and cannot generate a profit**
    
  - A player lands on "FREE PARKING"...
    - Depending on the version of the game being played, the player will either,
      - collect all money put into "FREE PARKING"
      - complete no type of action
    - **This tile cannot be bought and cannot generate a profit**
        
- After all players have rolled and moved, the next round begins and the process previously stated is repeated.

- The game ends when three of the four players run out of money and the player remaining wins.

##The Board
Note that you will need to download MonopolyBoard.csv in order for this code chunk to work.
```{r}
monopolyBoard <- read.csv("MonopolyBoard.csv", header = T)
monopolyBoard[is.na(monopolyBoard)] <- 0
monopolyBoard
```


_Lets Get Moving _
## lets_move
This section contains on the function lets_move which determines where a player will move to on the board. It does not incorporate any special movements such as double rolls, jail, or chance/community chest cards.

```{r Lets Get Moving}
#A function that uses dice rolls to determine where a player will land on the board
#input: "location", where the player is on the board
#output: the players new location on the board after the have rolled


lets_move = function(location) {
  dice_roll_1 <- sample(1:6, 1, replace = TRUE) #A random roll of a six-sided die
  dice_roll_2 <- sample(1:6, 1, replace = TRUE) #A random roll of a six-sided die
  
  roll_total <- sum(dice_roll_1, dice_roll_2) #The sum of the two rolls
  
  location = location + roll_total #Updating the player's location based on their rolls from the current turn
  
  if(location <= 40) { #if statement checking the players location
    location = location
  } else { #if the sum of the player's previous location and their rolls is greater than 40, this moves the player past GO and the start moving from space 1
    location = location - 40
  }
  
  #print(location)
  
}
```

## who_goes_first2
This section contains the function to determine which of the four players in the game will get to move first. Within the function, each player will roll two dice and take the sum of the rolls. The player with the highest sum gets to go first, and the next player is the player with the next numerical value (i.e. if player 3 has the highest sum, the order is: 3, 4, 1, 2). In the case of a tie, the players that are tied will continue to roll until they have different sums. 

```{r Let's Get Moving}
#A function to determine which of four players gets to roll first
#input: "num_players"; the number of players in the game
#output: "playerlist"; a list containing the player order

who_goes_first2 <- function(num_players){
  initial_rolls <- c()
  player_order <- length(num_players)
  for (i in 1:num_players) {
    player_i_roll <- sum(sample(1:6, 2, replace=TRUE))
    initial_rolls <- c(initial_rolls, player_i_roll) # vector of every player's first roll
  }
  
  if(sum(initial_rolls == max(initial_rolls)) >= 2){ # if more 1 person has the highest roll
    
    while (sum(initial_rolls == max(initial_rolls)) >= 2) { # keep rolling as long as players are tied
      tied_players <- which(initial_rolls==max(initial_rolls)) # identify which players tied

      tie_breaker_rolls <- c()
      for (i in tied_players) { # tied players roll again
       player_i_roll2 <- sum(sample(1:6, 2, replace=TRUE))
       tie_breaker_rolls <- c(tie_breaker_rolls, player_i_roll2)
       initial_rolls <- tie_breaker_rolls # update initial rolls
      }
    }
    highest_roll <- max(tie_breaker_rolls)
    highest_player <- tied_players[which(tie_breaker_rolls == highest_roll)]
  }
  
  else {
    highest_player <- which.max(initial_rolls) # who rolled the highest number
  
    # creating player order
    player_order[1] <- as.integer(highest_player)

    for (j in 2:num_players) {
    
      player_order[j] <- as.integer(player_order[j-1] + 1)
      if (player_order[j] > num_players) {
        player_order[j] <- 1
      }
    }
    #print(player_order)
  }
  playerlist <- (list(highest_player, player_order))
  playerlist
}
```

## lets_play
This section contains the function to play the game! lets_play utilizes both lets_move and who_goes_first2 to determine which player will start the game and each players location for each of the predetermined number of turns. While using the lets_play function, you can choose how many players you want to be in the game and how many turns you want the players to take. 

After all turns have been completed, lets_play will print three data frames showing all of the players locations through the game, the total number of times each property was landed on, and the total number of times each location was landed on. Additionally, it will a frequency plot showing the amount of times each property was landed on, a frequency plot showing the amount of times each location was landed on, a density plot of each players location data, a density plot showing the overall location data, and frequency plots for all of the players location data through out the game.

In the plots for "Frequency of Landing on each Property" and "Frequency of Landing on each Location" the colors of the bars represent the different colors associated with groups of properties or the type of location on a physical monopoly board. For example, the navy bars represent all Chance and Community Chest spaces on the board, light gray represent the utility properties, black represents all railroads, etc.

```{r Let's Get Moving}
#A function that allows players to move around the board while take turns for a set number of rounds

#input: "turns"; the amount of turns each player will take (i.e. the number of rounds in the game), "players"; a numeric value 1-4 representing the number of players in the game

#output: "location_data"; a data frame showing each players' location after each of their turns, "properties_landed"; a data frame showing the number of times each property was landed on; a frequency plot properties landed "locations_landed"; a data frame showing the number of times each location was landed on, a frequency plot showing the total number of times each property was landed on, a frequency plot showing the total number of times each location was landed on, a density plot showing each players' location data throughout the game, a density plot showing the overall location data throughout the game, a frequency plot for each players' location data

lets_play = function(turns, players) {
  
  location_data <- as.data.frame(matrix(nrow = turns, ncol = players)) # data frame that will keep data for locations of players for each turn
  
  # puts players in order
  colnames(location_data) <- who_goes_first2(players)[[2]]
  
  location = 1 #initializes the player at space 1 (i.e. GO!)
  location_data[1,] <- location

  for (i in 2:turns) { # iterates through number of turns
    for (j in 1:players) { # rotates through each player
      location = lets_move(location_data[i-1,j])[[1]] # takes location from lets_move2 function and assigns it to location
      location_data[i,j] <- as.integer(location) # puts location value into the data frame of locations for each player
    }
  }
  
#print(location_data) 

########################## property plot ###############################
properties_landed <- as.vector(as.matrix(location_data))

properties_landed <- properties_landed[properties_landed == 2 | properties_landed == 4 | properties_landed == 6 | properties_landed == 7 | properties_landed == 9 | properties_landed == 10 | properties_landed == 12 | properties_landed == 13 | properties_landed == 14 | properties_landed == 15 | properties_landed == 16 | properties_landed == 17 | properties_landed == 19 | properties_landed == 20 | properties_landed == 22 | properties_landed == 24 | properties_landed == 25 | properties_landed == 26 | properties_landed == 27 | properties_landed == 28 | properties_landed == 29 | properties_landed == 30 | properties_landed == 32 | properties_landed == 33 | properties_landed == 35 | properties_landed == 36 | properties_landed == 38 | properties_landed == 40]

property_names <- c("Mediterranean", "Baltic", "Reading Railroad", "Oriental", "Vermot", "Conecticut", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Tennessee", "New York", "Kentucky", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Pacific", "N. Carolina", "Pennsylvania", "Short Line Railroad", "Park Place", "Boardwalk")

properties_landed <- as.data.frame(properties_landed) 
properties_landed <- as.data.frame(properties_landed)
properties_landed <- properties_landed %>% group_by(properties_landed) %>% summarise(n())
properties_landed <- as.data.frame(properties_landed)
properties_landed <- cbind(property_names, properties_landed)
names(properties_landed) <- c("Property", "Location", "Occurances")
#print(properties_landed)

    colors_properties <- c("purple", "purple", "black", "lightblue", "lightblue", "lightblue", "violet", "lightgray", "violet", "violet", "black", "orange", "orange", "orange", "red", "red", "red", "black", "yellow", "yellow", "lightgray", "yellow", "darkgreen", "darkgreen", "darkgreen", "black", "blue", "blue")
    
    
  #creates a frequency plot for the number of times each property is landed on 
    property_plot <- ggplot(properties_landed, aes(x = Property, y = Occurances)) +
      geom_bar(stat = "identity", fill = colors_properties, color = "black") +
      scale_x_discrete(limits = properties_landed$Property) +
      ggtitle("Frequency of Landing on each Property") +
      xlab("Property") +
      ylab("Frequency") +
      theme(axis.text.x.bottom = element_text(angle=90, vjust = 0.001)) +
      scale_color_manual(name = "Properties",
                         breaks = c("Mediterranean", "Baltic", "Reading Railroad", "Oriental", "Vermot", "Conecticut", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Tennessee", "New York", "Kentucky", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Pacific", "N. Carolina", "Pennsylvania", "Short Line Railroad", "Park Place", "Boardwalk"),
                         values = colors_properties) 
    
    print(property_plot)
    
    
########################## location frequency plot ###############################
locations_landed <- as.vector(as.matrix(location_data))

location_names <- c("GO", "Mediterranean", "Community Chest 1", "Baltic ", "Income Tax", "Reading Railroad", "Oriental","Chance 1", "Vermot", "Conecticut", "Jail", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Community Chest 2", "Tennessee", "New York","Free Parking", "Kentucky", "Chance 2", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Go To Jail", "Pacific", "N. Carolina", "Community Chest 3", "Pennsylvania", "Short Line Railroad", "Chance 3", "Park Place", "Luxury Tax", "Boardwalk")

locations_landed <- as.data.frame(locations_landed) 
locations_landed <- as.data.frame(locations_landed)
locations_landed <- locations_landed %>% group_by(locations_landed) %>% summarise(n())
locations_landed <- as.data.frame(locations_landed)
locations_landed <- cbind(location_names, locations_landed)
names(locations_landed) <- c("Name", "Location", "Occurances")
#print(locations_landed)

    colors_locations <- c("white","purple","navy", "purple","white", "black", "lightblue","navy", "lightblue", "lightblue", "white", "violet", "lightgray", "violet", "violet", "black", "orange","navy", "orange", "orange","white", "red","navy", "red", "red", "black", "yellow", "yellow", "lightgray", "yellow","white", "darkgreen", "darkgreen","navy", "darkgreen", "black","navy", "blue","white", "blue")
    
    
  #creates a frequency plot for the number of times each property is landed on 
    location_plot <- ggplot(locations_landed, aes(x = Name, y = Occurances)) +
      geom_bar(stat = "identity", fill = colors_locations, color = "black") +
      scale_x_discrete(limits = locations_landed$Name) +
      ggtitle("Frequency of Landing on each Location") +
      xlab("Location") +
      ylab("Frequency") +
      theme(axis.text.x.bottom = element_text(angle=90, vjust = 0.001)) +
      scale_color_manual(name = "Properties",
                         breaks = c("GO", "Mediterranean", "Community Chest 1", "Baltic ", "Income Tax", "Reading Railroad", "Oriental","Chance 1", "Vermot", "Conecticut", "Jail", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Community Chest 2", "Tennessee", "New York","Free Parking", "Kentucky", "Chance 2", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Go To Jail", "Pacific", "N. Carolina", "Community Chest 3", "Pennsylvania", "Short Line Railroad", "Chance 3", "Park Place", "Luxury Tax", "Boardwalk"),
                         values = colors_locations) 
    
    print(location_plot)  

    
 ########################## location plots ###############################

 #vector of colors
  colors <- c("red", "blue", "green","purple")
  
  # creates density plot of frequency of landing on each space for each player
  plot(density(location_data[,1]), xlim = c(0,40), col = "black", xlab="Spaces", main= "Distribution of Landing of Different Monopoly Spaces")
  
  for (k in 2:players) {
    lines(density(location_data[,k]), col = colors[k-1]) # adds a density line for each player after the first
  }
  
  # creates density plot for total frequency landing on each space (all players spaces included)
 all_spaces <- as.vector(as.matrix(location_data))
 # plot(density(all_spaces), xlim = c(0,40), col = "black", xlab="Spaces", main="Density of Landing Locations Overall")
  
  #creates frequency plot for frequency of landing on certain spaces for each player
  #for(k in 1:players){
 # plot(location_data[,k], xlim= c(0,40), col=colors[k], type="h", xlab="Spaces", ylab="Frequency", main="Frequency of Landing on Each Space for Each Player")
 # }

 # plot frequencies of landing on each space
  plot(all_spaces, xlim = c(0,40), col = "blue", type="h", xlab = "Spaces", ylab = "Frequency", main = "Frequency of Landing on Monopoly Spaces")
  
  # second set of frequency plots for individual player locations
   # colors2 <- c("coral1", "steelblue1", "palegreen2","plum2")
   # freq_data <- data.frame(space = 1:40, freq = tabulate(location_data[, 1], nbins = 40))
   # density_plot <- ggplot(freq_data, aes(x = space, y = freq)) +
   #  geom_bar(stat = "identity", fill = colors2[1], color = "black") +
   #  ggtitle(paste0("Player Frequency of Landing on Each Space")) +
   #  xlab("Spaces") +
   #  ylab("Frequency") +
   #  theme_minimal()
    
   # print(density_plot)
}

lets_play(1000, 4)


```


_Double Down_ 
##lets_move2
This section contains the function lets_move2 that expands on lets_move by adding the ability for players to go to jail and to utilize double rolls while playing. !WARNING! If you roll three doubles in a row you'll be sent in jail!

```{r Double Down}
#Double Down -- addition of jail and double rolls

#Incorporating double rolls and sending players to jail when the players are rolling and moving
#input: "location"; a numeric value 1 to 40; where the player in on the board
#output: "listdata"; a list containing the player's new location on the board and if the player rolled doubles three times in a row.

lets_move2 = function(location) {
  dice_roll_1 <- sample(1:6, 1, replace = TRUE) #a standard, six-sided dice roll
  dice_roll_2 <- sample(1:6, 1, replace = TRUE) #a standard, six-sided dice roll
  
  roll_total <- sum(dice_roll_1, dice_roll_2) #the sum of the two dice rolls
  roll_double <- dice_roll_1 == dice_roll_2 #checking if the player rolled a double
  
    location = location + roll_total # updates location to be previous location + roll total
    double3 = "false" # double3 is assigned "true" if the player double rolls 3x (as seen in if statement below), otherwise it is assigned "false" 
    
  # first double roll -> roll again
  if (roll_double == TRUE) { #checks if the player rolled a double with their first two rolls. if "TRUE", the player rolls again
    dice_roll_3 <- sample(1:6, 1, replace = TRUE) #the player's third dice roll
    dice_roll_4 <- sample(1:6, 1, replace = TRUE) #the player's fourth dice roll
    
    roll_total2 <- sum(dice_roll_3, dice_roll_4) #the sum of the player's third and fourth rolls
    roll_double2 <- dice_roll_3 == dice_roll_4 #checks to see if the player rolled a double again
    
    location = location + roll_total2 #the player's new location
    double3 = "false"
    
    # if player is at a location past 40, subtract 40 so they go back to the GO space at location "41"
    # this is included in each if statement below so that it applies if player has to roll again
    if (location <= 40) { #checks to make sure that the player's location isn't over 40 (i.e not on the board)
      location = location
    } else { #If greater than 40, it subtracts 40 from location to allow player to continue to move on the board
      location = location - 40
    }
     
      # second double roll -> roll again
      if (roll_double2 == TRUE) { #if the player has rolled two doubles, they roll again
        dice_roll_5 <- sample(1:6, 1, replace = TRUE) #the player's fifth roll
        dice_roll_6 <- sample(1:6, 1, replace = TRUE) #the player's sixth roll
    
        roll_total3 <- sum(dice_roll_5, dice_roll_6) #the sum of the fifth and sixth roll
        roll_double3 <- dice_roll_5 == dice_roll_6 #checking to see if the player rolled a third double
    
        location = location + roll_total3 #the players new location
        double3 = "false"
        
        if (location <= 40) { #checks the player's location again
          location = location
        } else {
          location = location - 40
        }
        
        # third double roll -> go to jail
          if (roll_double3 == TRUE) { #checks if the player rolled three doubles in a row, if TRUE, the players goes to jail (space 11)
            location = monopolyBoard$spaces[monopolyBoard$name == "Jail"]
            double3 = "true"
          }
      }
  }  
    
  if (location <= 40) { #checks the players location on the board
    location = location
  } else {
    location = location - 40
  }
  
  listdata <- (list(location, double3)) # creates list for outputs "location" and "double3"
  # if you need to access location from this function, use lets_move2(location_data[i-1,j])[[1]]
  # if you need to access double3, use lets_move2(double3)[[2]]
  return(listdata)
  
}
```

## lets_play2
This section contains the function lets_play2 which incorporates lets_move2 and who_goes_first2 to determine which player will start the game and each players location for each of the predetermined number of turns. This is an updated version of lets_play where players are now able to roll doubles and go to jail. While using the lets_play2 function, you can choose how many players you want to be in the game and how many turns you want the players to take. 

After all turns have been completed, lets_play2 will print three data frames showing all of the players locations through the game, the total number of times each property was landed on, and the total number of times each location was landed on. Additionally it will print a frequency plot showing the amount of times each property was landed on, a frequency plot showing the amount of times each location was landed on, a density plot of each players location data, a density plot showing the overall location data, and frequency plots for all of the players location data through out the game.

In the plots for "Frequency of Landing on each Property" and "Frequency of Landing on each Location" the colors of the bars represent the different colors associated with groups of properties or the type of location on a physical monopoly board. For example, the navy bars represent all Chance and Community Chest spaces on the board, light gray represent the utility properties, black represents all railroads, etc.

```{r Double Down}
#A function to move players around the board while incorporating double rolls and going to jail

#input: "turns"; the amount of turns each player takes (i.e. how many rounds the game is), "players"; a numeric value 1-4 representing the number of players in the game

#output: "location_data"; a data frame showing each players' location after each of their turns, "properties_landed"; a data frame showing the number of times each property was landed on; a frequency plot properties landed "locations_landed"; a data frame showing the number of times each location was landed on, a frequency plot showing the total number of times each property was landed on, a frequency plot showing the total number of times each location was landed on, a density plot showing each players' location data throughout the game, a density plot showing the overall location data throughout the game, a frequency plot for each players' location data

lets_play2 = function(turns, players) {
  
  
  location_data <- as.data.frame(matrix(nrow = turns, ncol = players)) # dataframe will keep data for locations of players for each turn
  double3data <- as.data.frame(matrix(nrow = turns, ncol = players)) # dataframe will say "true" if player double rolled 3x (which lands them in jail) and "false" if they didn't double roll 3x
  
    # puts players in order
    colnames(location_data) <- who_goes_first2(players)[[2]]
  
    location = 1 # each player starts at location 1
    location_data[1,] <- location
    double3 = 0 # initializing "double3" which will be later assigned a "true" or "false" based on if player double rolled 3x
  
    for (i in 2:turns) { # iterates through number of turns
      
        for (j in 1:players) { # rotates through each player
          
        location = lets_move2(location_data[i-1,j])[[1]] # takes location from lets_move2 function and assigns it to location
        location_data[i,j] <- as.integer(location) # puts location value into the dataframe of locations for each player
        double3data[i,j] <- lets_move2(double3)[[2]] # takes "true" or "false" value from double3 and adds it to double3data dataframe
        
      # deals with landing in jail from "go to jail" space and staying there for next 3 turns
      if (31 %in% location_data[i-1,j]) { # if you landed on 31 in the last turn (i-1 turn), you go to jail (space 11) for the ith turn
        location <- 11
        location_data[i,j] <- as.integer(location) # new location is 11
      } else if (11 %in% location_data[i-1,j] & 31 %in% location_data[i-2,j]) { # if you were on space 11 last turn AND you were on space 31 2 turns ago, you stay in jail (space 11) for turn i
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & 31 %in% location_data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
      # landing in jail from 3x double roll and staying there for next 3 turns
      if (11 %in% location_data[i,j] & "true" %in% double3data[i-1,j]) { # if player's location is 11 (jail) and double3data is"true" (player double rolled 3x), player stays in jail. all 3 if/else if statements keep player in jail for the next 3 turns
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & "true" %in% double3data[i-2,j]) { # 
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & "true" %in% double3data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
    }
  }
  #print(location_data)
  #print(double3)
  
  
########################## property plot ###############################
  
properties_landed <- as.vector(as.matrix(location_data))

properties_landed <- properties_landed[properties_landed == 2 | properties_landed == 4 | properties_landed == 6 | properties_landed == 7 | properties_landed == 9 | properties_landed == 10 | properties_landed == 12 | properties_landed == 13 | properties_landed == 14 | properties_landed == 15 | properties_landed == 16 | properties_landed == 17 | properties_landed == 19 | properties_landed == 20 | properties_landed == 22 | properties_landed == 24 | properties_landed == 25 | properties_landed == 26 | properties_landed == 27 | properties_landed == 28 | properties_landed == 29 | properties_landed == 30 | properties_landed == 32 | properties_landed == 33 | properties_landed == 35 | properties_landed == 36 | properties_landed == 38 | properties_landed == 40]

property_names <- c("Mediterranean", "Baltic", "Reading Railroad", "Oriental", "Vermot", "Conecticut", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Tennessee", "New York", "Kentucky", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Pacific", "N. Carolina", "Pennsylvania", "Short Line Railroad", "Park Place", "Boardwalk")

properties_landed <- as.data.frame(properties_landed) 
properties_landed <- as.data.frame(properties_landed)
properties_landed <- properties_landed %>% group_by(properties_landed) %>% summarise(n())
properties_landed <- as.data.frame(properties_landed)
properties_landed <- cbind(property_names, properties_landed)
names(properties_landed) <- c("Property", "Location", "Occurances")
#print(properties_landed)

    colors_properties <- c("purple", "purple", "black", "lightblue", "lightblue", "lightblue", "violet", "lightgray", "violet", "violet", "black", "orange", "orange", "orange", "red", "red", "red", "black", "yellow", "yellow", "lightgray", "yellow", "darkgreen", "darkgreen", "darkgreen", "black", "blue", "blue")
    
    
  #creates a frequency plot for the number of times each property is landed on 
    property_plot <- ggplot(properties_landed, aes(x = Property, y = Occurances)) +
      geom_bar(stat = "identity", fill = colors_properties, color = "black") +
      scale_x_discrete(limits = properties_landed$Property) +
      ggtitle("Frequency of Landing on each Property") +
      xlab("Property") +
      ylab("Frequency") +
      theme(axis.text.x.bottom = element_text(angle=90, vjust = 0.001)) +
      scale_color_manual(name = "Properties",
                         breaks = c("Mediterranean", "Baltic", "Reading Railroad", "Oriental", "Vermot", "Conecticut", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Tennessee", "New York", "Kentucky", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Pacific", "N. Carolina", "Pennsylvania", "Short Line Railroad", "Park Place", "Boardwalk"),
                         values = colors_properties)
    
    print(property_plot)

    
########################## location frequency plot ###############################
locations_landed <- as.vector(as.matrix(location_data))

location_names <- c("GO", "Mediterranean", "Community Chest 1", "Baltic ", "Income Tax", "Reading Railroad", "Oriental","Chance 1", "Vermot", "Conecticut", "Jail", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Community Chest 2", "Tennessee", "New York","Free Parking", "Kentucky", "Chance 2", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Go To Jail", "Pacific", "N. Carolina", "Community Chest 3", "Pennsylvania", "Short Line Railroad", "Chance 3", "Park Place", "Luxury Tax", "Boardwalk")

locations_landed <- as.data.frame(locations_landed) 
locations_landed <- as.data.frame(locations_landed)
locations_landed <- locations_landed %>% group_by(locations_landed) %>% summarise(n())
locations_landed <- as.data.frame(locations_landed)
locations_landed <- cbind(location_names, locations_landed)
names(locations_landed) <- c("Name", "Location", "Occurances")
#print(locations_landed)

    colors_locations <- c("white","purple","navy", "purple","white", "black", "lightblue","navy", "lightblue", "lightblue", "white", "violet", "lightgray", "violet", "violet", "black", "orange","navy", "orange", "orange","white", "red","navy", "red", "red", "black", "yellow", "yellow", "lightgray", "yellow","white", "darkgreen", "darkgreen","navy", "darkgreen", "black","navy", "blue","white", "blue")
    
    
  #creates a frequency plot for the number of times each property is landed on 
    location_plot <- ggplot(locations_landed, aes(x = Name, y = Occurances)) +
      geom_bar(stat = "identity", fill = colors_locations, color = "black") +
      scale_x_discrete(limits = locations_landed$Name) +
      ggtitle("Frequency of Landing on each Location") +
      xlab("Location") +
      ylab("Frequency") +
      theme(axis.text.x.bottom = element_text(angle=90, vjust = 0.001)) +
      scale_color_manual(name = "Properties",
                         breaks = c("GO", "Mediterranean", "Community Chest 1", "Baltic ", "Income Tax", "Reading Railroad", "Oriental","Chance 1", "Vermot", "Conecticut", "Jail", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Community Chest 2", "Tennessee", "New York","Free Parking", "Kentucky", "Chance 2", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Go To Jail", "Pacific", "N. Carolina", "Community Chest 3", "Pennsylvania", "Short Line Railroad", "Chance 3", "Park Place", "Luxury Tax", "Boardwalk"),
                         values = colors_locations) 
    
    print(location_plot)  
    
    
########################## location plots ###############################

 #vector of colors
  colors <- c("red", "blue", "green","purple")
  
  # creates density plot of frequency of landing on each space for each player
  plot(density(location_data[,1]), xlim = c(0,40), col = "black", xlab="Spaces", main= "Distribution of Landing on Different Monopoly Spaces")
  
  for (k in 2:players) {
    lines(density(location_data[,k]), col = colors[k-1]) # adds a density line for each player after the first
  }
  
  # creates density plot for total frequency landing on each space (all players spaces included)
  all_spaces <- as.vector(as.matrix(location_data))
  #plot(density(all_spaces), xlim = c(0,40), col = "black", xlab="Spaces", main="Density of Landing Locations Overall")
  
  #creates frequency plot for frequency of landing on certain spaces for each player
 # for(k in 1:players){
 # plot(location_data[,k], xlim= c(0,40), col=colors[k], type="h", xlab="Spaces", ylab="Frequency", main="Frequency of Landing on Each Space for Each Player")
 # }
  
 plot(all_spaces, xlim = c(0,40), col = "blue", type="h", xlab = "Spaces", ylab = "Frequency", main = "Frequency of Landing on Monopoly Spaces")
  
  # second set of frequency plots for individual player locations
  #for (k in 1:players) {
  #  colors <- c("coral1", "steelblue1", "palegreen2","plum2")
  #  freq_data <- data.frame(space = 1:40, freq = tabulate(location_data[, k], nbins = 40))
  #  density_plot <- ggplot(freq_data, aes(x = space, y = freq)) +
  #   geom_bar(stat = "identity", fill = colors[k], color = "black") +
  #   ggtitle(paste0("Player ", k, ": Frequency of Landing on Each Space")) +
  #   xlab("Spaces") +
  #   ylab("Frequency") +
  #   theme_minimal()
    
  #  print(density_plot)
  #}
 
}
 
lets_play2(1000, 4)
```


_Take a Chance_
##The Community Chest and Chance Cards
This section contains the data frames for both the Chance and Community Chest cards. Each data frame contains 16 cards, each of which have a description. 

```{r Take a Chance}

Card_Numbers <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16) # the card numbers

Chance_Cards <- c("Advance to Boardwalk", "Advance to Go (Collect $200)", "Advance to Illinois Avenue. If you pass Go, collect $200", "Advance to St. Charles Place. If you pass Go, collect $200", "Advance to the nearest Railroad. If unowned, you may buy it from the Bank. If owned, pay owner twice the rental to which they are otherwise entitled", "Advance to the nearest Railroad. If unowned, you may buy it from the Bank. If owned, pay owner twice the rental to which they are otherwise entitled", "Advance token to nearest Utility. If unowned, you may buy it from the Bank. If owned, throw dice and pay owner a total ten times amount thrown", "Bank pays you dividend of $50", "Get Out of Jail Free", "Go Back 3 Spaces", "Go to Jail. Go directly to Jail, do not pass Go, do not collect $200", "Make general repairs on all your property. For each house pay $25. For each hotel pay $100", "Speeding fine $15", "Take a trip to Reading Railroad. If you pass Go, collect $200", "You have been elected Chairman of the Board. Pay each player $50", "Your building loan matures. Collect $150") # the card information

Chance <- data.frame(Chance_Cards, Card_Numbers) #a dataframe associating each chance card with a number



Community_Chest_Cards <- c("Advance to Go (Collect $200)", "Bank error in your favor. Collect $200", "Doctor’s fee. Pay $50", "From sale of stock you get $50", "Get Out of Jail Free", "Go to Jail. Go directly to jail, do not pass Go, do not collect $200", "Holiday fund matures. Receive $100", "Income tax refund. Collect $20", "It is your birthday. Collect $10 from every player", "Life insurance matures. Collect $100", "Pay hospital fees of $100", "Pay school fees of $50", "Receive $25 consultancy fee", "You are assessed for street repair. $40 per house. $115 per hotel", "You have won second prize in a beauty contest. Collect $10", "You inherit $100") # the card information

Community_Chest <- data.frame(Community_Chest_Cards, Card_Numbers) #a dataframe associating each community chest card with a number
```

##Drawing_Chance and Drawing_Community_Chest
This section contains the functions Drawing_Chance and Drawing_Community_Chest. If a player lands on a Chance or Community Chest space, these functions will randomly select on of the sixteen cards from the respective deck. Most of these cards will either update the player's location or the player's bank (player banks are added and discussed later in _Play a Game_). 

```{r Taking a Chance}
#A function that randomly selects a numeric value 1:16 representing a Chance card and updates the player's location based on the card information
#input: "location"; a numeric value 1:40 representing the player's location on the board
#output: "list_location_amount"; a list contain the player's updated location and the amount that their bank will be changed by (note that amount will not be used in lets_move3 and lets_play3, it is used in lets_move4 and lets_play4)

Drawing_Chance = function(location) {
  location = location #the player's current location
  amount <- 0 #amount is later used to updated the player's bank in lets_play4
  amount2 <- 0 #amount2 is later used to update free parking in lets_play5
  draw_card <- sample(1:16, 1, replace = TRUE) #randomly selecting a card from 1:16 cards
  player_card <- Chance$Chance_Cards[draw_card] #finding the card in the Chance deck

#The following if statements update the player's location based on the card that was drawn (if applicable)  
      if(draw_card == 1) { # Advance to Boardwalk
        location = 1
      }
      
      if(draw_card == 2) { # Advance to Go (Collect $200)
        location = 1
        amount = 200
      }
      
      if(draw_card == 3) { #Advance to Illinois Avenue. If you pass Go, collect $200
        if(location > 25){
          amount = 200
        }else{
          amount = amount
    }
        location = 25
      }
  
      if(draw_card == 4){ # Advance to St. Charles Place. If you pass Go, collect $200
        if(location > 13 ){
          amount = 200
        }else{
          amount = amount
    }
        location = 12
      }
  
      if(draw_card == 5){ # Advance to the nearest Railroad.
        if(location >= 37 && location <= 5){
              location = 6
            } else {
              if (location >= 6 && location <= 15){
                location = 16
              } else {
                if(location >= 16 && location <= 25){
                  location = 26
                } else {
                  location = 36
                }
              }
            }
    }
  
    if(draw_card == 6){ # Advance to the nearest Railroad.
        if(location >= 37 && location <= 5){
              location = 6
            } else {
              if (location >= 6 && location <= 15){
                location = 16
              } else {
                if(location >= 16 && location <= 25){
                  location = 26
                } else {
                  location = 36
                }
              }
            }
    }
  
    if(draw_card == 7){ #	Advance token to nearest Utility.
        if(location >= 29 && location <= 12){
              location = 13
            } else {
              location = 29
    }
    }
  
    if(draw_card == 8){ #Bank pays you dividend of $50
      amount = 50
    }
  
    if(draw_card == 10) { #Go Back 3 Spaces
      location = location - 3
    }
  
    if(draw_card == 11) { #Go to Jail. Go directly to Jail
      location = 11
    }
  
    if(draw_card == 13){ #Speeding fine $15
      amount = -15
      amount2 = 15
    }
  
    if(draw_card == 14) { #Take a trip to Reading Railroad.
      if(location > 6){
        amount = 200
      }else{
        amount = amount
    }
      location = 6
    }
  
    if(draw_card == 16){ #Your building loan matures.
      amount = 150
    }
  
   
    location = location
    amount = amount
    amount2 = amount2
    list_location_amount <- list(location, amount, amount2)
    return(list_location_amount)
}



#A function that randomly selects a numeric value 1:16 representing a Community Chest card and updates the player's location based on the card information
#input: "location"; a numeric value 1:40 representing the player's location on the board
#output: the player's new location on the board

Drawing_Community_Chest = function(location) {
  location = location
  amount <- 0
  amount2 <- 0
  draw_card_chest <- sample(1:16, 1, replace = TRUE)
  player_card_chest <- Community_Chest$Community_Chest_Cards[draw_card_chest]
  
  
  if (draw_card_chest == 1) { # Advance to Go (Collect $200)
    location = 1
    amount = 200
  }
  
  #Bank error in your favor. Collect $200
  if(draw_card_chest == 2){
    amount = 200
  }
  
  #Doctor’s fee. Pay $50
  if(draw_card_chest == 3){
    amount = -50
    amount2 = 50
  }
  
  #From sale of stock you get $50
  if(draw_card_chest == 4){
    amount = 50
  }
  
  if(draw_card_chest == 6) { # Go to Jail
    location = 11
  }
  
  #Holiday fund matures. Receive $100
  if(draw_card_chest == 7){
    amount = 100
  }
  
  #Income tax refund. Collect $20
  if(draw_card_chest == 8){
    amount = 20
  }
  
  #Life insurance matures. Collect $100
  if(draw_card_chest == 10){
    amount = 100
  }
  
  #Pay hospital fees of $100
  if(draw_card_chest == 11){
    amount = -100
    amount2 = 100
  }
  
  #Pay school fees of $50
  if(draw_card_chest == 12){
    amount = -50
    amount2 = 50
  }
  
  #Receive $25 consultancy fee
  if(draw_card_chest == 13){
    amount = 25
  }
  
  #You have won second prize in a beauty contest. Collect $10
  if(draw_card_chest == 15){
    amount = 10
  }
  
  #You inherit $100
  if(draw_card_chest == 16){
    amount = 100
  }
  
  location = location 
  amount = amount
  amount2 = amount2
  list_location_amount <- list(location,amount,amount2)
  return(list_location_amount)
}
```


## lets_move3
This section contains that function lets_move3 which utilizes Drawing_Chance and Drawing_Community  to draw either a Chance or Community chest card when a player lands on a Chance or Community Chest space.

```{r Take a Chance}
#A function that expands on lets_move2 to add the actions of Community Chest and Chance spaces and their respective cards
#input: "location"; a numeric value 1 to 40; where the player in on the board
#output: "listdata"; a list containing the player's new location on the board and if the player rolled doubles three times in a row.

lets_move3 = function(location) {
  dice_roll_1 <- sample(1:6, 1, replace = TRUE)
  dice_roll_2 <- sample(1:6, 1, replace = TRUE)
  
  roll_total <- sum(dice_roll_1, dice_roll_2)
  roll_double <- dice_roll_1 == dice_roll_2
  
    location = location + roll_total
    double3 = "false"


  if (location <= 40) {
      location = location
      amount = 0
  } else {
      location = location - 40
      amount = 200
  }
   
  
  if(location == 8 || location == 23 || location == 27) { #if the player lands on a Chance space, they draw a Chance card
    location = Drawing_Chance(location)[[1]]
  }
  
  if(location == 3 || location == 18 || location == 34) { #if the player lands on a Community Chest space, they draw a Community Chest card
    location = Drawing_Community_Chest(location)[[1]]
  }
    
  # first double roll -> roll again
  if (roll_double == TRUE) {
    dice_roll_3 <- sample(1:6, 1, replace = TRUE)
    dice_roll_4 <- sample(1:6, 1, replace = TRUE)
    
    roll_total2 <- sum(dice_roll_3, dice_roll_4)
    roll_double2 <- dice_roll_3 == dice_roll_4
    
    location = location + roll_total2
    double3 = "false"
    
    if (location <= 40) {
      location = location
      amount = 0
    } else {
      location = location - 40
      amount = 200
    }
    
    
    if(location == 8 || location == 23 || location == 27) { #if the player lands on a Chance space, they draw a Chance card
    location = Drawing_Chance(location)[[1]]
    }
  
  if(location == 3 || location == 18 || location == 34) { #if the player lands on a Community Chest space, they draw a Community Chest card
    location = Drawing_Community_Chest(location)[[1]]
    }
     
      # second double roll -> roll again
      if (roll_double2 == TRUE) {
        dice_roll_5 <- sample(1:6, 1, replace = TRUE)
        dice_roll_6 <- sample(1:6, 1, replace = TRUE)
    
        roll_total3 <- sum(dice_roll_5, dice_roll_6)
        roll_double3 <- dice_roll_5 == dice_roll_6
    
        location = location + roll_total3
        double3 = "false"
        
        if (location <= 40) {
          location = location
          amount = 0
        } else {
          location = location - 40
          amount = 200
        }
        
        if(location == 8 || location == 23 || location == 27) { #if the player lands on a Chance space, they draw a Chance card
          location = Drawing_Chance(location)[[1]]
        }
  
        if(location == 3 || location == 18 || location == 34) { #if the player lands on a Community Chest space, they draw a Community Chest card
          location = Drawing_Community_Chest(location)[[1]]
         
        }
        
        # third double roll -> go to jail
          if (roll_double3 == TRUE) {
            location = monopolyBoard$spaces[monopolyBoard$name == "Jail"]
            double3 = "true"

          }
      }
  }  
   
  location = location 

  listdata <- (list(location, double3, amount)) # creates list for outputs "location" and "double3"
  # if you need to access location from this function, use lets_move3(location_data[i-1,j])[[1]]
  # if you need to access double3, use lets_move3(double3)[[2]]
  return(listdata)
  
}


```

##lets_play3

This section contains the function lets_play3 which incorporates lets_move3 and who_goes_first2 to determine which player will start the game and each players location for each of the predetermined number of turns. This is an updated version of lets_play3 where players are now able use the Chance and Community Chest spaces. While using the lets_play2 function, you can choose how many players you want to be in the game and how many turns you want the players to take. 

After all turns have been completed, lets_play3 will print three data frames showing all of the players locations through the game, the total number of times each property was landed on, and the total number of times each location was landed on. Additionally, it will print a frequency plot showing the amount of times each property was landed on, a frequency plot showing the amount of times each location was landed on, a density plot of each players location data, a density plot showing the overall location data, and frequency plots for all of the players location data through out the game.

In the plots for "Frequency of Landing on each Property" and "Frequency of Landing on each Location" the colors of the bars represent the different colors associated with groups of properties or the type of location on a physical monopoly board. For example, the navy bars represent all Chance and Community Chest spaces on the board, light gray represent the utility properties, black represents all railroads, etc.

```{r Take a Chance}
#A function to move players around the board while incorporating chance and community chest cards and their effects

#input: "turns"; the amount of turns each player takes (i.e. how many rounds the game is), "players"; a numeric value 1-4 representing the number of players in the game

#output: "location_data"; a data frame showing each players' location after each of their turns, "properties_landed"; a data frame showing the number of times each property was landed on, "locations_landed"; a data frame showing the number of times each location was landed on, a frequency plot showing the total number of times each property was landed on, a frequency plot showing the total number of times each location was landed on, a density plot showing each players' location data throughout the game, a density plot showing the overall location data throughout the game, a frequency plot for each players' location data

lets_play3 = function(turns, players) {
  
  location_data <- as.data.frame(matrix(nrow = turns, ncol = players))
  double3data <- as.data.frame(matrix(nrow = turns, ncol = players))
  
    colnames(location_data) <- who_goes_first2(players)[[2]]
  
    location = 1
    location_data[1,] <- location
    double3 = 0
  
    for (i in 2:turns) {
      
        for (j in 1:players) {
          
        location = lets_move3(location_data[i-1,j])[[1]]
        location_data[i,j] <- as.integer(location)
        double3data[i,j] <- lets_move3(double3)[[2]]
        
      # deals with landing in jail from "go to jail" space and staying there for next 3 turns
      if (31 %in% location_data[i-1,j]) { # if you land on 31 (go to jail), next location is in jail (space 11)
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & 31 %in% location_data[i-2,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & 31 %in% location_data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
      # landing in jail from 3x double roll and staying there for next 3 turns
      if (11 %in% location_data[i,j] & "true" %in% double3data[i-1,j]) { # "true" means player double rolled 3x -> jail
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & "true" %in% double3data[i-2,j]) { # 
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & "true" %in% double3data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
    }
  }
  #print(location_data)
  #print(double3data)

  
  
########################## property plot ###############################
properties_landed <- as.vector(as.matrix(location_data))

properties_landed <- properties_landed[properties_landed == 2 | properties_landed == 4 | properties_landed == 6 | properties_landed == 7 | properties_landed == 9 | properties_landed == 10 | properties_landed == 12 | properties_landed == 13 | properties_landed == 14 | properties_landed == 15 | properties_landed == 16 | properties_landed == 17 | properties_landed == 19 | properties_landed == 20 | properties_landed == 22 | properties_landed == 24 | properties_landed == 25 | properties_landed == 26 | properties_landed == 27 | properties_landed == 28 | properties_landed == 29 | properties_landed == 30 | properties_landed == 32 | properties_landed == 33 | properties_landed == 35 | properties_landed == 36 | properties_landed == 38 | properties_landed == 40]

property_names <- c("Mediterranean", "Baltic", "Reading Railroad", "Oriental", "Vermot", "Conecticut", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Tennessee", "New York", "Kentucky", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Pacific", "N. Carolina", "Pennsylvania", "Short Line Railroad", "Park Place", "Boardwalk")

properties_landed <- as.data.frame(properties_landed) 
properties_landed <- as.data.frame(properties_landed)
properties_landed <- properties_landed %>% group_by(properties_landed) %>% summarise(n())
properties_landed <- as.data.frame(properties_landed)
properties_landed <- cbind(property_names, properties_landed)
names(properties_landed) <- c("Property", "Location", "Occurances")
#print(properties_landed)

    colors_properties <- c("purple", "purple", "black", "lightblue", "lightblue", "lightblue", "violet", "lightgray", "violet", "violet", "black", "orange", "orange", "orange", "red", "red", "red", "black", "yellow", "yellow", "lightgray", "yellow", "darkgreen", "darkgreen", "darkgreen", "black", "blue", "blue")
    
    #creates a frequency plot for the number of times each property is landed on 
    property_plot <- ggplot(properties_landed, aes(x = Property, y = Occurances)) +
      geom_bar(stat = "identity", fill = colors_properties, color = "black") +
      scale_x_discrete(limits = properties_landed$Property) +
      ggtitle("Frequency of Landing on each Property") +
      xlab("Property") +
      ylab("Frequency") +
      theme(axis.text.x.bottom = element_text(angle=90, vjust = 0.001)) +
      scale_color_manual(name = "Properties",
                         breaks = c("Mediterranean", "Baltic", "Reading Railroad", "Oriental", "Vermot", "Conecticut", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Tennessee", "New York", "Kentucky", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Pacific", "N. Carolina", "Pennsylvania", "Short Line Railroad", "Park Place", "Boardwalk"),
                         values = colors_properties)
    
    print(property_plot)
  
      

########################## location frequency plot ###############################
locations_landed <- as.vector(as.matrix(location_data))

location_names <- c("GO", "Mediterranean", "Community Chest 1", "Baltic ", "Income Tax", "Reading Railroad", "Oriental","Chance 1", "Vermot", "Conecticut", "Jail", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Community Chest 2", "Tennessee", "New York","Free Parking", "Kentucky", "Chance 2", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Go To Jail", "Pacific", "N. Carolina", "Community Chest 3", "Pennsylvania", "Short Line Railroad", "Chance 3", "Park Place", "Luxury Tax", "Boardwalk")

locations_landed <- as.data.frame(locations_landed) 
locations_landed <- as.data.frame(locations_landed)
locations_landed <- locations_landed %>% group_by(locations_landed) %>% summarise(n())
locations_landed <- as.data.frame(locations_landed)
locations_landed <- cbind(location_names, locations_landed)
names(locations_landed) <- c("Name", "Location", "Occurances")
#print(locations_landed)

    colors_locations <- c("white","purple","navy", "purple","white", "black", "lightblue","navy", "lightblue", "lightblue", "white", "violet", "lightgray", "violet", "violet", "black", "orange","navy", "orange", "orange","white", "red","navy", "red", "red", "black", "yellow", "yellow", "lightgray", "yellow","white", "darkgreen", "darkgreen","navy", "darkgreen", "black","navy", "blue","white", "blue")
    
    
  #creates a frequency plot for the number of times each property is landed on 
    location_plot <- ggplot(locations_landed, aes(x = Name, y = Occurances)) +
      geom_bar(stat = "identity", fill = colors_locations, color = "black") +
      scale_x_discrete(limits = locations_landed$Name) +
      ggtitle("Frequency of Landing on each Location") +
      xlab("Location") +
      ylab("Frequency") +
      theme(axis.text.x.bottom = element_text(angle=90, vjust = 0.001)) +
      scale_color_manual(name = "Properties",
                         breaks = c("GO", "Mediterranean", "Community Chest 1", "Baltic ", "Income Tax", "Reading Railroad", "Oriental","Chance 1", "Vermot", "Conecticut", "Jail", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Community Chest 2", "Tennessee", "New York","Free Parking", "Kentucky", "Chance 2", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Go To Jail", "Pacific", "N. Carolina", "Community Chest 3", "Pennsylvania", "Short Line Railroad", "Chance 3", "Park Place", "Luxury Tax", "Boardwalk"),
                         values = colors_locations) 
    
    print(location_plot)  
    
    
        
########################## location plots ###############################    
  
  # creates density plot of frequency of landing on each space for each player
  colors <- c("red", "blue", "green","purple")
  
  plot(density(location_data[,1]), xlim = c(0,40), col = "black", xlab="Spaces", main= "Density of Landing Locations for All Players")
  
  for (k in 2:players) {
    lines(density(location_data[,k]), col = colors[k-1]) # adds a density line for each player after the first
  }
  
  # creates density plot for total frequency landing on each space (all players spaces included)
  all_spaces <- as.vector(as.matrix(location_data))
  #plot(density(all_spaces), xlim = c(0,40), col = "blue", xlab="Spaces", main="Density of Landing Locations Overall")
  
 # for(k in 1:players){
 #plot(location_data[,k], xlim= c(0,40), col=colors[k], type="h", xlab="Spaces", ylab="Frequency", main="Frequency of Landing on Each Space for Each Player")
#  }
  
  plot(all_spaces, xlim = c(0,40), col = "blue", type="h", xlab = "Spaces", ylab = "Frequency", main = "Frequency of Landing Locations Overall")
  
  # second set of frequency plots for individual player locations
  #for (k in 1:players) {
  #  colors <- c("coral1", "steelblue1", "palegreen2","plum2")
  #  freq_data <- data.frame(space = 1:40, freq = tabulate(location_data[, k], nbins = 40))
  #  density_plot <- ggplot(freq_data, aes(x = space, y = freq)) +
  #   geom_bar(stat = "identity", fill = colors[k], color = "black") +
  #   ggtitle(paste0("Player ", k, ": Frequency of Landing on Each Space")) +
  #   xlab("Spaces") +
  #   ylab("Frequency") +
  #   theme_minimal()
    
  #  print(density_plot)
  #}
  
}

lets_play3(1000,4)


```


_Play a Game_

##lets_move4
This section contains the function lets_move4 which is an updated version of lets_move3. Players now will collect $200 every time they pass "GO" (space 1). Additionally, this function utilizes the "amount" object that certain cards in Drawing_Chance and Drawing_Community Chest contain which affects the player's bank later in lets_play4.

```{r Play a Game}
#A function that expands on lets_move3 to add the collection of $200 every time a player passes "Go"
#input: "location"; a numeric value 1 to 40; where the player in on the board
#output: "listdata"; a list that contains location (the player's updated location), double3 (if the player rolled doubles three times in a row), and amount (a money value that may affect the player's bank)

lets_move4 = function(location) {
  dice_roll_1 <- sample(1:6, 1, replace = TRUE) 
  dice_roll_2 <- sample(1:6, 1, replace = TRUE) 
  
  roll_total <- sum(dice_roll_1, dice_roll_2)
  roll_double <- dice_roll_1 == dice_roll_2
  
    location = location + roll_total
    double3 = "false"


  if (location <= 40) {
      location = location
      amount = 0
  } else {
      location = location - 40
      amount = 200
  }
   
  
  if(location == 8 || location == 23 || location == 27) { #check's if the player's location is a Chance space
    location = Drawing_Chance(location)[[1]] #if TRUE, the player draws a Chance card using the Drawing_Chance function which updates their location
  }
  
  if(location == 3 || location == 18 || location == 34) { #check's if the player's location is a Community Chest space
    location = Drawing_Community_Chest(location)[[1]] #if TRUE, the player draws a Community Chest card using the Drawing_Community_Chest which updates their location
  }
    
  # first double roll -> roll again
  if (roll_double == TRUE) {
    dice_roll_3 <- sample(1:6, 1, replace = TRUE)
    dice_roll_4 <- sample(1:6, 1, replace = TRUE)
    
    roll_total <- sum(dice_roll_3, dice_roll_4)
    roll_double2 <- dice_roll_3 == dice_roll_4
    
    location = location + roll_total
    double3 = "false"
    
    if (location <= 40) {
      location = location
      amount = 0
    } else {
      location = location - 40
      amount = 200
    }
    
    
    if(location == 8 || location == 23 || location == 27) { #check's if the player's location is a Chance space
    location = Drawing_Chance(location)[[1]] #if TRUE, the player draws a Chance card using the Drawing_Chance function which updates their location
    }
  
  if(location == 3 || location == 18 || location == 34) { #check's if the player's location is a Community Chest space
    location = Drawing_Community_Chest(location)[[1]] #if TRUE, the player draws a Community Chest card using the Drawing_Community_Chest which updates their location
    }
     
      # second double roll -> roll again
      if (roll_double2 == TRUE) {
        dice_roll_5 <- sample(1:6, 1, replace = TRUE)
        dice_roll_6 <- sample(1:6, 1, replace = TRUE)
    
        roll_total <- sum(dice_roll_5, dice_roll_6)
        roll_double3 <- dice_roll_5 == dice_roll_6
    
        location = location + roll_total
        double3 = "false"
        
        if (location <= 40) {
          location = location
          amount = 0
        } else {
          location = location - 40
          amount = 200
        }
        
        if(location == 8 || location == 23 || location == 27) { #check's if the player's location is a Chance space
          location = Drawing_Chance(location)[[1]] #if TRUE, the player draws a Chance card using the Drawing_Chance function which updates their location
        }
  
        if(location == 3 || location == 18 || location == 34) { #check's if the player's location is a Community Chest space
          location = Drawing_Community_Chest(location)[[1]] #if TRUE, the player draws a Community Chest card using the Drawing_Community_Chest which updates their location
         
        }
        
        # third double roll -> go to jail
          if (roll_double3 == TRUE) {
            location = monopolyBoard$spaces[monopolyBoard$name == "Jail"]
            double3 = "true"

          }
        
      }
  }  
   
  location = location 

  listdata <- (list(location, double3, amount))
  return(listdata)
  
}

```

##lets_play4
This section contains the function lets_play4. This function expands on lets_play3 by adding players' banks. While using the lets_play4 function, you can choose how many players you want to be in the game and how many turns you want the players to take. 

Within lets_play4, the first step is to create the player banks in a data frame called The_Players and to determine which players own which properties in a data frame called Property_Statuses. Then, as the player's are progressing through their turns, the respective banks of the player who lands on a location and the player who owns the location are updated based on the property's rent. In addition, if the player lands on a Chest or Community Chest space, they may earn money or have to pay depending on what card they drew. 

After all turns have been completed, lets_play4 will print the phrase "The game lasted _ turns." Using this output, we created a loop to run 100 games and from this sample we found that the average game length is 51.33 or approximately 52 turns.

```{r Play a Game}
#A function to move players around the board while incorporating player banks

#input: "turns"; the amount of turns each player takes (i.e. how many rounds the game is), "players"; a numeric value 1-4 representing the number of players in the game

#output: "The game lasted i turns"; a phrase statement how many turns the game lasted where i = the number of turns each player took

lets_play4 = function(turns, players) {
  
  #creates the player banks
  Players <- c("Player 1", "Player 2", "Player 3", "Player 4")
  Player_Bank <- c(1500, 1500, 1500, 1500)
  The_Players <- data.frame(Players, Player_Bank)
  
  #determines which players own which properties
  Property <- c("Mediterranean", "Baltic", "Reading Railroad", "Oriental", "Vermot", "Connecticut", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Tennessee", "New York", "Kentucky", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Pacific", "N. Carolina", "Pennsylvania", "Short Line Railroad", "Park Place", "Boardwalk")
  Owned_By_Player <- sample(1:4, 28, replace = TRUE)
  Space <- c(2, 4, 6, 7, 9, 10, 12, 13, 14, 15, 16, 17, 19, 20, 22, 24, 25, 26, 27, 28, 29, 30, 32, 33, 35, 36, 38, 40)
  Property_Statuses <- data.frame(Property, Space, Owned_By_Player)

  setting_player_banks = function(players) {
    for(m in 1:players) {
      for (n in 1:28) {
        owned <- Property_Statuses$Owned_By_Player[n]
        spot <- Property_Statuses$Space[n]
        payment <- monopolyBoard$cost[spot]
        The_Players$Player_Bank[owned] = The_Players$Player_Bank[owned] - payment
        The_Players = The_Players
    }
   The_Players = The_Players
   return(The_Players)
    }
  }

  
  location_data <- as.data.frame(matrix(nrow = turns, ncol = players))
  double3data <- as.data.frame(matrix(nrow = turns, ncol = players))
  players_with_0 <- vector(length = players) # For later use; stopping function when only 1 player has money
  
    colnames(location_data) <- who_goes_first2(players)[[2]]
  
    location = 1
    location_data[1,] <- location
    double3 = 0
  
    for (i in 2:turns) {
      
        for (j in 1:players) {
          
        location = lets_move4(location_data[i-1,j])[[1]]
        location_data[i,j] <- as.integer(location)
        double3data[i,j] <- lets_move4(location)[[2]]
        
      # deals with landing in jail from "go to jail" space and staying there for next 3 turns
      if (31 %in% location_data[i-1,j]) { # if you land on 31 (go to jail), next location is in jail (space 11)
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & 31 %in% location_data[i-2,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & 31 %in% location_data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
      # landing in jail from 3x double roll and staying there for next 3 turns
      if (11 %in% location_data[i,j] & "true" %in% double3data[i-1,j]) { # "true" means player double rolled 3x -> jail
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & "true" %in% double3data[i-2,j]) { # 
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & "true" %in% double3data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }

        
      # updating banks if players land on each others' properties
      if(location %in% c(2, 4, 7, 9, 10, 12, 13, 14, 15, 17, 19, 20, 22, 24, 25, 27, 28, 29, 30, 32, 33, 35, 38, 40)) {
            
      location = location
      spot <- which(Property_Statuses$Space == location)
      cost <- which(monopolyBoard$spaces == location)
      owned_by_player <- Property_Statuses$Owned_By_Player[spot]
        
      The_Players$Player_Bank[owned_by_player] <- The_Players$Player_Bank[owned_by_player] + monopolyBoard$rent_3[cost]
      The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] - monopolyBoard$rent_4[cost]
      }
      
      #updating banks if players land on others' railroads
      if(location %in% c(6, 16, 26, 36)){
        
      location = location
      spot <- which(Property_Statuses$Space == location)
      cost <- which(monopolyBoard$spaces == location)
      owned_by_player <- Property_Statuses$Owned_By_Player[spot]
        
      The_Players$Player_Bank[owned_by_player] <- The_Players$Player_Bank[owned_by_player] + 200
      The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] - 200
      }
      
      # Updating player bank if they gained or lost money from a Chance card
      if (Drawing_Chance(location_data[i,j])[[2]] != 0) {
        The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] + Drawing_Chance(location_data[i,j])[[2]]  
      }
        
      # Updating player bank if they gained or lost money from a Community Chest card 
      if (Drawing_Community_Chest(location_data[i,j])[[2]] != 0) {
        The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] + Drawing_Community_Chest(location_data[i,j])[[2]]  
      }
      
      # Player gets $200 if they pass go
      if (lets_move3(location_data[i,j])[[3]] != 0) {
        The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] + lets_move3(location_data[i,j])[[3]]  
      }
      
      # Paying when player lands on a tax space
      if (5 %in% location_data[i,j] || 39 %in% location_data[i,j]) {
        The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] - monopolyBoard$cost[location_data[i,j]] # subtracting cost of tax from player's bank
      }
    
        
    ##################    
    # Stopping the game when only 1 player has money left:
  
    # If a player has <= $0, make their bank equal to 0 and put their player number in vector players_with_0 
    if (The_Players$Player_Bank[j] <= 0) {
      The_Players$Player_Bank[j] = 0
      players_with_0[j] <- j
    }
    
    # If player j is in vectors_with_0 (indicating that they have hit $0), continue to make their bank = 0 each turn
    if (j %in% players_with_0) {
      The_Players$Player_Bank[j] = 0
    }
  }
    # assign the number of zeros in players_with_0 to count_of_0 
    count_of_0 <- length(which(players_with_0 %in% 0))
    
    # If only 1 player has a 0 in players_with_0 (indicating that they still have money), print the banks of each player and stop the game
    if (count_of_0 == 1) {
      i=i
      print(paste("The game lasted", i, "turns."))
      break
    }
    
  }
  
  #print(location_data)
}


lets_play4(1000, 4)

game_lengths <- numeric()

for(m in 1:100) {
  lengths <- lets_play4(1000, 4)[m]
  game_lengths <- c(game_lengths, lengths)
}
```

This code chunk contains 100 sample game lengths from lets_play4 to find the average game length.
```{r}
lengths_of_games_lets_play4<-c(11,
46,
8,
9,
103,
8,
12,
79,
32,
7,
22,
22,
104,
29,
25,
62,
17,
104,
18,
20,
18,
75,
40,
20,
21,
92,
27,
15,
89,
10,
24,
91,
12,
28,
775,
9,
13,
29,
28,
72,
44,
12,
13,
12,
12,
13,
12,
10,
34,
9,
22,
11,
28,
11,
36,
47,
36,
41,
12,
13,
25,
152,
120,
61,
14,
39,
31,
9,
33,
42,
28,
36,
28,
17,
103,
16,
13,
95,
12,
393,
38,
60,
15,
877,
56,
18,
58,
18,
72)

avg_game_lengths_lets_play4 <- sum(lengths_of_games_lets_play4)/100
avg_game_lengths_lets_play4
```

##lets_play5
This section contains the function lets_play5 which expands on lets_play4 to include the action of potentially modifying a player's bank if they land on Free Parking (space 21). While using the lets_play5 function, you can choose how many players you want to be in the game and how many turns you want the players to take. 

Every payment that a player makes that would go to the general bank rather than another player is now paid to Free Parking. Then, if a player lands on Free Parking, they receive the amount of money stored in the Free_Parking data frame. Free_Parking is then reset to 0 and can immediately begin accumulating money again. 

This function prints the phrase, "This game lasted _ turns." Using this output, we created a loop to run 100 games and from this sample we found that the average game length when including free parking is 35.97 or approximately 36 games.

```{r}
#A function to move players around the board while incorporating player banks

#input: "turns"; the amount of turns each player takes (i.e. how many rounds the game is), "players"; a numeric value 1-4 representing the number of players in the game

#output: "The game lasted i turns"; a phrase statement how many turns the game lasted where i = the number of turns each player took

lets_play5 = function(turns, players) {
  
  #creates the player banks
  Players <- c("Player 1", "Player 2", "Player 3", "Player 4")
  Player_Bank <- c(1500, 1500, 1500, 1500)
  The_Players <- data.frame(Players, Player_Bank)
  
  #determines which players own which properties
  Property <- c("Mediterranean", "Baltic", "Reading Railroad", "Oriental", "Vermot", "Connecticut", "St. Charles", "Electric Company", "States", "Virginia", "Pennsylvania Railroad", "St. James", "Tennessee", "New York", "Kentucky", "Indiana", "Illinios", "B&O Railroad", "Atlantic", "Ventnor", "Water Works", "Marvin Gardens", "Pacific", "N. Carolina", "Pennsylvania", "Short Line Railroad", "Park Place", "Boardwalk")
  Owned_By_Player <- sample(1:4, 28, replace = TRUE)
  Space <- c(2, 4, 6, 7, 9, 10, 12, 13, 14, 15, 16, 17, 19, 20, 22, 24, 25, 26, 27, 28, 29, 30, 32, 33, 35, 36, 38, 40)
  Property_Statuses <- data.frame(Property, Space, Owned_By_Player)

  setting_player_banks = function(players) {
    for(m in 1:players) {
      for (n in 1:28) {
        owned <- Property_Statuses$Owned_By_Player[n]
        spot <- Property_Statuses$Space[n]
        payment <- monopolyBoard$cost[spot]
        The_Players$Player_Bank[owned] = The_Players$Player_Bank[owned] - payment
        The_Players = The_Players
    }
   The_Players = The_Players
   return(The_Players)
    }
  }

      #creates the free parking bank
    free_parking <- c("Free Parking")
    bank <- c(0)
    Free_Parking <- data.frame(free_parking, bank)
    
  location_data <- as.data.frame(matrix(nrow = turns, ncol = players))
  double3data <- as.data.frame(matrix(nrow = turns, ncol = players))
  players_with_0 <- vector(length = players) # For later use; stopping function when only 1 player has money
  
    colnames(location_data) <- who_goes_first2(players)[[2]]
  
    location = 1
    location_data[1,] <- location
    double3 = 0
  
    for (i in 2:turns) {
      
        for (j in 1:players) {
          
        location = lets_move4(location_data[i-1,j])[[1]]
        location_data[i,j] <- as.integer(location)
        double3data[i,j] <- lets_move4(location)[[2]]
        
      # deals with landing in jail from "go to jail" space and staying there for next 3 turns
      if (31 %in% location_data[i-1,j]) { # if you land on 31 (go to jail), next location is in jail (space 11)
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & 31 %in% location_data[i-2,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & 31 %in% location_data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }
        
      # landing in jail from 3x double roll and staying there for next 3 turns
      if (11 %in% location_data[i,j] & "true" %in% double3data[i-1,j]) { # "true" means player double rolled 3x -> jail
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-1,j] & "true" %in% double3data[i-2,j]) { # 
        location <- 11
        location_data[i,j] <- as.integer(location)
      } else if (11 %in% location_data[i-2,j] & "true" %in% double3data[i-3,j]) {
        location <- 11
        location_data[i,j] <- as.integer(location)
      }

        
      # updating banks if players land on each others' properties
      if(location %in% c(2, 4, 7, 9, 10, 12, 13, 14, 15, 17, 19, 20, 22, 24, 25, 27, 28, 29, 30, 32, 33, 35, 38, 40)) {
            
      location = location
      spot <- which(Property_Statuses$Space == location)
      cost <- which(monopolyBoard$spaces == location)
      owned_by_player <- Property_Statuses$Owned_By_Player[spot]
        
      The_Players$Player_Bank[owned_by_player] <- The_Players$Player_Bank[owned_by_player] + monopolyBoard$rent_3[cost]
      The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] - monopolyBoard$rent_4[cost]
      }
      
      #updating banks if players land on others' railroads
      if(location %in% c(6, 16, 26, 36)){
        
      location = location
      spot <- which(Property_Statuses$Space == location)
      cost <- which(monopolyBoard$spaces == location)
      owned_by_player <- Property_Statuses$Owned_By_Player[spot]
        
      The_Players$Player_Bank[owned_by_player] <- The_Players$Player_Bank[owned_by_player] + 200
      The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] - 200
      }
      
      # Updating player bank if they gained or lost money from a Chance card
      if (Drawing_Chance(location_data[i,j])[[2]] != 0) {
        The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] + Drawing_Chance(location_data[i,j])[[2]]  
      }
        
      # Updating player bank if they gained or lost money from a Community Chest card 
      if (Drawing_Community_Chest(location_data[i,j])[[2]] != 0) {
        The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] + Drawing_Community_Chest(location_data[i,j])[[2]]  
      }
      
      # Player gets $200 if they pass go
      if (lets_move3(location_data[i,j])[[3]] != 0) {
        The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] + lets_move3(location_data[i,j])[[3]]  
      }
      
      # Paying when player lands on a tax space
      if (5 %in% location_data[i,j] || 39 %in% location_data[i,j]) {
        The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] - monopolyBoard$cost[location_data[i,j]] # subtracting cost of tax from player's bank
      }
        
      #Free Parking payments
      if (21 %in% location_data[i,j]) {
        The_Players$Player_Bank[j] <- The_Players$Player_Bank[j] + Free_Parking$bank
        Free_Parking$bank <- 0
      }
    
        
    ##################    
    # Stopping the game when only 1 player has money left:
  
    # If a player has <= $0, make their bank equal to 0 and put their player number in vector players_with_0 
    if (The_Players$Player_Bank[j] <= 0) {
      The_Players$Player_Bank[j] = 0
      players_with_0[j] <- j
    }
    
    # If player j is in vectors_with_0 (indicating that they have hit $0), continue to make their bank = 0 each turn
    if (j %in% players_with_0) {
      The_Players$Player_Bank[j] = 0
    }
  }
    # assign the number of zeros in players_with_0 to count_of_0 
    count_of_0 <- length(which(players_with_0 %in% 0))
    
    # If only 1 player has a 0 in players_with_0 (indicating that they still have money), print the banks of each player and stop the game
    if (count_of_0 == 1) {
      i=i
      print(paste("The game lasted", i, "turns."))
      break
    }
    
  }
  
  #print(location_data)
}


lets_play5(1000, 4)

game_lengths <- numeric()

for(m in 1:100) {
  lengths <- lets_play5(1000, 4)[m]
  game_lengths <- c(game_lengths, lengths)
  game_lengths <- as.data.frame(game_lengths)
}


```

The code chunk contains the 100 sample game lengths from lets_play5 to find the average game length. 
```{r}
lengths_of_games_lets_play5 <- c(17, 29, 18,
19,
15,
36,
14,
12,
20,
31,
114,
11,
37,
23,
12,
18,
21,
13,
54,
13,
8,
36,
134,
30,
79,
10,
18,
41,
16,
61,
10,
12,
26,
48,
27,
15,
180,
311,
9,
14,
28,
61,
32,
23,
14,
107,
14,
122,
76,
13,
15,
83,
67,
29,
101,
18,
10,
30,
45,
20,
15,
94,
16,
30,
57,
11,
26,
13,
49,
11,
22,
16,
23,
64,
32,
35,
35,
10,
32,
94,
16,
18,
29,
17,
21,
18,
122,
24,
29,
44,
21,
33)

avg_game_lengths_lets_play5 <- sum(lengths_of_games_lets_play5)/100
avg_game_lengths_lets_play5
```


